### 2019-05-02 sections/introduction.tex
fix new par in introduction
fix typos suggested by the reviewers
clarify sentence structure

\MTASKS is a subset of \ITASKS,
focussing on \IOT devices and deployment on micro controllers.
It has been used to control home thermostats and other home automation applications \cite{koopman2018task}.
%
Both implementations currently lack formal semantics which are suited to prove properties about tasks.

@@

\begin{enumerate*}
  \item
    We describe the essential concepts of task-oriented programming.
  \item
    We present a formal language for modelling declarative workflows, embedded in a simply typed $lambda$-calculus, called \TOPHAT.
    It is based on the aforementioned essential \TOP concepts.
  \item
    We develop a layered operational semantics for \TOPHAT that is driven by user input.
    The semantics of the task language is clearly separated from the semantics of the underlying host language.
  \item
    Along with this semantics, we present the following semantic observations on tasks:
    the current value, whether a term is stuck, the current user interface, and the accepted inputs.
  \item
    We prove progress and type preservation for \TOPHAT.
  \item
    Using both the essential concepts and the formal language, we compare \TOP with related work in areas ranging from business process modelling, to process algebras and reactive programming.

  \item
    We implemented the whole semantic system in the dependently typed programming language Idris \cite{journals/jfp/Brady13}.
  \item
    To create executable applications, we implemented the task layer of \TOPHAT in iTasks.
    This also demonstrates that the former is a subset of the latter.
\end{enumerate*}

>>>>

\MTASKS is a subset of \ITASKS,
focusing on \IOT devices and deployment on micro controllers.
It has been used to control home thermostats and other home automation applications \cite{koopman2018task}.
%
Both implementations currently lack formal semantics which are suited to prove properties about tasks.

@@

\begin{enumerate*}
  \item
    We describe the essential concepts of task-oriented programming.
  \item
    We present a formal language for modelling declarative workflows, called \TOPHAT, embedded in a simply typed $\lambda$-calculus.
    It is based on the aforementioned essential \TOP concepts.
  \item
    We develop a layered operational semantics for \TOPHAT that is driven by user input.
    The semantics of the task language is clearly separated from the semantics of the underlying host language.
  \item
    Along with this semantics, we present the following semantic observations on tasks:
    the current value, whether a term is stuck, the current user interface, and the accepted inputs.
  \item
    We prove progress and type preservation for \TOPHAT.
  \item
    Using both the essential concepts and the formal language, we compare \TOP with related work in areas ranging from business process modelling, to process algebras and reactive programming.
  \item
    We implemented the whole semantic system in the dependently typed programming language Idris \cite{journals/jfp/Brady13}.
  \item
    To create executable applications, we implemented the task layer of \TOPHAT in iTasks.
    This also demonstrates that the former is a subset of the latter.
\end{enumerate*}
